Enforced Invariant Confluence

### 2020-01-19 doc/the_vldb_journal_paper/sections/evaluation.tex
Formatted captions for Journal requirements.
They don't want punctuation at the end of a caption, and they want table
captions to describe the contents.

\begin{figure}[t]
  \centering
  \includegraphics[width=\columnwidth]{figures/throughput_vs_fraction_16.pdf}
  \caption{%
    Segmented \invariantconfluent{} replication throughput versus coordination
    induced by executing disallowed decrement transactions.
  }\figlabel{ThroughputVsGlobalSyncs}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=\columnwidth]{figures/throughput_vs_num_nodes_multi.pdf}
  \caption{%
    Throughput of eventually consistent, segmented \invariantconfluent{}, and
    linearizable replication measured against the number of nodes for workloads
    with varying fractions of decrement transactions. For example, the
    ``segmented (0.2)'' line measures the performance of segmented
    \invariantconfluent{} replication with 20\% decrement transactions.
    Eventually consistent replication and linearizable replication are not
    affected by workload.
  }\figlabel{VaryNodes}
\end{figure}

>>>>

\begin{figure}[t]
  \centering
  \includegraphics[width=\columnwidth]{figures/throughput_vs_fraction_16.pdf}
  \caption{%
    Segmented \invariantconfluent{} replication throughput versus coordination
    induced by executing disallowed decrement transactions
  }\figlabel{ThroughputVsGlobalSyncs}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=\columnwidth]{figures/throughput_vs_num_nodes_multi.pdf}
  \caption{%
    Throughput of eventually consistent, segmented \invariantconfluent{}, and
    linearizable replication measured against the number of nodes for workloads
    with varying fractions of decrement transactions. For example, the
    ``segmented (0.2)'' line measures the performance of segmented
    \invariantconfluent{} replication with 20\% decrement transactions.
    Eventually consistent replication and linearizable replication are not
    affected by workload
  }\figlabel{VaryNodes}
\end{figure}
